Communication in Agile Inter-team Development

### 2019-01-21 Draft/Parts/Main.tex
Added SOS ref.

\section{Communication Concerns}\label{sec:spt_ex} 
%overview
A fundamental issue in tasking teams with separate goals is that teams can become isolated from other teams pursuing similar or related goals.
% problem
Consider a scenario at Spotify \cite{kniberg12}: a tester on a particular agile team invested time to solve a particular problem, which was also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters, which are crosscutting groups which gather individuals with similar roles across different Squads. 
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close.
This leads to an environment where an informal exchange of information on the Tribe's work will occur.
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
%todo: any more issues? Dunbar

@@

%Changes in standups
One critical aspect of an agile process is daily standups which are a platform for letting each team member know the work being done in other parts of the team and correlate it with the work they are performing.
This uncovers differences in understanding early in development and prevents last minute discovery of discrepancies.
In the case of multiple agile teams this problem is compounded as a stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other.
This can be resolved by having a representative of each concerned team be present in the daily standup thus letting each team know the status of the other teams.

>>>>

\section{Communication Concerns}\label{sec:spt_ex} 
%overview
A fundamental issue in tasking teams with separate goals is that teams can become isolated from other teams pursuing similar or related goals.
% problem
Consider a scenario at Spotify \cite{kniberg12}: a tester on a particular agile team invested time to solve a particular problem, which was also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters, which are crosscutting groups which gather individuals with similar roles across different Squads. 
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close.
This leads to an environment where an informal exchange of information on the Tribe's work will occur.
%Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
%todo: any more issues? Dunbar

@@

%Changes in standups
One critical aspect of an agile process is daily standups which are a platform for letting each team member know the work being done in other parts of the team and correlate it with the work they are performing.
This uncovers differences in understanding early in development and prevents last minute discovery of discrepancies.
In the case of multiple agile teams this problem is compounded as a stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other.
This can be resolved by having a representative of each team be present in a standup, e.g., a Scrum of Scrums, where typical stand up questions are given but reframed for a team context (e.g., "What will my team do before we meet again.." \cite{Rubin12}).
